### 2018-07-03 doc/plos/text/manuscript.tex
add sensor fitting subsection

\begin{description}
  \item{\textbf{Google Flu Trends}} \\
    Google Flu Trends was a weekly prediction of wILI based on Google searches.
    The service was originally released in 2008; was updated in 2009, 2013, and
    2014 \cite{ginsberg2009, gft_main}; and was discontinued in 2015.
  \item{\textbf{Google Health Trends}} \\
    Google Health Trends is an API by Google for research purposes which makes
    available, among many other things, daily counts (on an arbitrary scale)
    for a predefined influenza topic. TODO(link)
  \item{\textbf{HealthTweets}} \\
    HealthTweets (http://healthtweets.org) makes available the daily volume of
    tweets indicative of ILI \cite{broniatowski2013national,
    dredze2014healthtweets}.
  \item{\textbf{Wikimedia Foundation}} \\
    The Wikimedia Foundation makes available the number of hits, per hour, to
    every Wikipedia article. TODO(link)
  \item{\textbf{CDC Page Hits}} \\
    CDC makes available the number of daily hits per page, per state for their
    website (https:/www.cdc.gov/).
\end{description}

@@

%As others have done for flu and other infectious diseases
%\cite{generous2014global, hickmann2015forecasting, mciver2014wikipedia}, we use
%the popularity of selected articles to estimate wILI for the US as a whole.
%
%As with WIKI, we use popularity of selected pages to estimate ILI within US
%states.
%
%Inputs available at sub-weekly temporal resolution are aggregated to form
%weekly readings.

>>>>

\begin{description}
  \item{\textbf{Google Flu Trends (GFT)}} \\
    Google Flu Trends was a weekly prediction of wILI based on Google searches.
    The service was originally released in 2008; was updated in 2009, 2013, and
    2014 \cite{ginsberg2009, gft_main}; and was discontinued in 2015.
  \item{\textbf{Google Health Trends (GHT)}} \\
    Google Health Trends is an API by Google for research purposes which makes
    available, among many other things, daily counts (on an arbitrary scale)
    for a predefined influenza topic. TODO(link)
  \item{\textbf{HealthTweets (TWTR)}} \\
    HealthTweets (http://healthtweets.org) makes available the daily volume of
    tweets indicative of ILI \cite{broniatowski2013national,
    dredze2014healthtweets}.
  \item{\textbf{Wikimedia Foundation (WIKI)}} \\
    The Wikimedia Foundation makes available the number of hits, per hour, to
    every Wikipedia article. TODO(link)
  \item{\textbf{CDC Page Hits (CDCP)}} \\
    CDC makes available the number of daily hits per page, per state for their
    website (https:/www.cdc.gov/).
\end{description}

@@

To obtain a signal usable for nowcasting, we must fit inputs to wILI. Since
this is trivially the case for predictive surveillance (i.e. EPIC, SAR3, and
ARCH), we use those values directly. For digital survaillance, we use
historical data to build a linear regression model mapping raw inputs to wILI.
We then apply this model with the most recent data to obtain a prediction of
wILI. We repeat the fitting procedure each week prior to nowcasting to obtain a
new model based on the most up-to-date data. The fitting procedure is described
in more detail in \cite{farrow2016modeling}.

Data sources with a single covariate (i.e. GFT, GHT, TWTR) are fit with
ordinary linear regression. Data sources with multiple covariates (i.e. WIKI,
CDCP) are fit with multiple linear regression.

As others have done for flu and other infectious diseases
\cite{generous2014global, hickmann2015forecasting, mciver2014wikipedia}, we use
the volume of Wikipedia traffic to estimate wILI for the US as a whole. To
produce a signal, we fit seven covariates to wILI, each corresponding to a
particular flu-releated Wikipedia article. The articles TODO(list in SI) were
chosen offline and by hand \textit{a priori}. Since WIKI has no attached
location information, we filter by particular hours of the day TODO(list in SI)
as a very rough proxy of Wikipedia activity in the US. Although this is a
grossly invalid assumption, preliminary investigation showed this to provide a
better fit to wILI.

Similarly, CDCP consists of six covariates, each corresponding to a particular
flu-releated page on the CDC website. The pages TODO(list in SI) were chosen
offline and by hand \textit{a priori}. CDCP is unique in that the covariates
are log-transformed before fitting as preliminary investigation showed this to
provide a better fit to wILI.

For all digital surveillance sources, we apply the fitting procedure separately
for each available location (e.g. US as a whole, HHS regions, census divisions,
and US states).

For data sources with sub-weekly temporal resolution (i.e. GHT, TWTR, WIKI,
CDCP), we aggregate counts by week before applying the fitting procedure. In
future work we aim to incorporate these sources as soon as they are available,
rather than waiting until the end of the week to use their aggregate values.
